Really Good Title

### 2019-01-07 documentation/paper.tex
Small fixes

A big advantage of the neuroevolution scheme is that for a series of different inputs a single scalar indicator of performance is sufficient to optimize a neural network for a certain task.
This can for instance be given by the outcome of a game.
Our game of choice is Blobby Volley 2 which is an open source, simple two-dimensional volleyball game written in C++ with lua support. See Figure \ref{fig:screenshot}.

@@

The game comes bundled with a number of bots with different styles, that are designed to pose a challenge to a wide range of human opponents. In order to define a clean ranking between them, we recorded the score of all possible lineups. The results can be seen in table no. \ref{tab:bot_vs_bot}.
\todo{explain the table}

@@

We implemented our own bot to act as an initial trainer \texttt{trainer} for the network.
This trainer is easier to defeat.
We made a copy of each bot where it gives up after a certain amount of touches with the ball, such that normal gameplay will be rewarded.
The simplification gives the evolutionary algorithm the opportunity to start optimizing the neural network in a valid direction, without introducing additional factors to the fitness score.

>>>>

A big advantage of the neuroevolution scheme is that for a series of different inputs a single scalar indicator of performance is sufficient to optimize a neural network for a certain task.
This can for instance be given by the outcome of a game.
Our game of choice is Blobby Volley 2 which is an open source, simple two-dimensional volleyball game written in C++ with lua support. Example picture in figure \ref{fig:screenshot}.

@@

The game comes bundled with a number of bots with different styles, that are designed to pose a challenge to a wide range of human opponents. In order to define a clean ranking between them, we recorded the score of all possible lineups (figure \ref{tab:bot_vs_bot}).
\todo{explain the table}

@@

We implemented our own bot marked \texttt{trainer} to act as an initial trainer for the network.
This trainer is easier to defeat than the other built-in players.
The simplification gives the evolutionary algorithm the opportunity to start optimizing the neural network in a valid direction, without introducing additional factors to the fitness score.
